Union and Intersection Contracts Are Hard, Actually

### 2021-09-16 paper.tex
Fix ACM metadata

%%% The following is specific to DLS '21 and the paper
%%% 'Union and Intersection Contracts Are Hard, Actually'
%%% by Teodoro Freund, Yann Hamdaoui, and Arnaud Spiwack.
\copyrightyear{2021}
\acmYear{2021}
\setcopyright{acmlicensed}\acmConference[DLS '21]{Proceeding of the 17th ACM SIGPLAN International Symposium on Dynamic Languages}{October 19, 2021}{Chicago, IL, USA}
\acmBooktitle{Proceeding of the 17th ACM SIGPLAN International Symposium on Dynamic Languages (DLS '21), October 19, 2021, Chicago, IL, USA}
\acmPrice{15.00}
\acmDOI{10.1145/3486602.3486767}
\acmISBN{978-1-4503-9105-4/21/10}

\acmConference[DLS '21]{Proceedings of the 17th ACM SIGPLAN International Symposium on Dynamic Languages}{October 19, 2021}{Chicago, IL, USA}
\acmBooktitle{Proceedings of the 17th ACM SIGPLAN International Symposium on Dynamic Languages (DLS '21), October 19, 2021, Chicago, IL, USA}

>>>>

%%% The following is specific to DLS '21 and the paper
%%% 'Union and Intersection Contracts Are Hard, Actually'
%%% by Teodoro Freund, Yann Hamdaoui, and Arnaud Spiwack.
\setcopyright{acmlicensed}
\acmPrice{15.00}
\acmDOI{10.1145/3486602.3486767}
\acmYear{2021}
\copyrightyear{2021}
\acmSubmissionID{splashws21dlsmain-p31-p}
\acmISBN{978-1-4503-9105-4/21/10}
\acmConference[DLS '21]{Proceedings of the 17th ACM SIGPLAN International Symposium on Dynamic Languages}{October 19, 2021}{Chicago, IL, USA}
\acmBooktitle{Proceedings of the 17th ACM SIGPLAN International Symposium on Dynamic Languages (DLS '21), October 19, 2021, Chicago, IL, USA}
